The Private School Network

### 2024-02-25 index.qmd
added Patricia Martin cite

- Institutional financial aid to convert admits [@RN3762]
- Recruiting interventions at earlier stages of enrollment funnel
  - "Student list" purchases [@RN4985]
  - Off-campus recruiting visits [@RN4758; @RN4934]
    - Out-of-state visits to public high schools focus on affluent public schools, avoid non-white communities

>>>>

- Institutional financial aid to convert admits [@RN3762]
- Recruiting interventions at earlier stages of enrollment funnel
  - "Student list" purchases [@list_biz; @RN4985]
  - Off-campus recruiting visits [@RN4758; @RN4934]
    - Out-of-state visits to public high schools focus on affluent public schools, avoid non-white communities
